
%%=============================================================================
%% Samenvatting engels
%%=============================================================================
\chapter*{Samenvatting English}

In my second and final year of the Programming course at HOGENT, 
I had to complete a graduation project. This had to be a project in 
collaboration with my internship company. Together with Victor Buyck 
Steel Construction, a steel construction company in Eeklo, we decided 
to develop a reception application.
\bigskip
The company was paying annually for an external SaaS solution to manage 
their reception. The problem was that this solution regularly went down 
and that the annual cost was high. Because of this, the decision was made 
to develop their own solution.

\bigskip
The result is WelcomeDesk, a reception application consisting of a 
Blazor frontend and a C\#-backend. Visitors can check in by filling in 
their details and selecting an employee. That employee is then automatically 
notified via a Teams message, an SMS and an email.
\bigskip
Blazor was chosen for the development because the company was already 
familiar with it and actively uses it in other internal projects. An 
additional advantage of Blazor WebAssembly is that the application can 
run as a standalone app in the browser without needing a constant server 
connection. This makes the application more stable and easier to deploy 
on a device at the reception. The data is stored in a MySQL database. 
The Teams notifications are handled via Power Automate, the SMS via Proximus.

\bigskip
WelcomeDesk is a working replacement for the old paid solution. 
The licence cost is eliminated, the system is more stable and it can 
easily be extended in the future if needed.
